%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

%\section{Publications}
\cvsection{Publications}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

%\cventry
%{Journal papers} % Job title
%{} % Organization
%{} % Location
%{} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%
%\item {\textbf{Tinghuan Chen}, Bingqing Lin, Hao Geng, Shiyan Hu, Bei Yu, ``Leveraging Spatial Correlation for Sensor Drift Calibration in Smart Building'', accepted by \textbf{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD)}.}
%
%\item {Qianru Zhang, Meng Zhang, \textbf{Tinghuan Chen}, Zhifei Sun, Yuzhe Ma and Bei Yu. ``Recent advances in convolutional neural network acceleration". \textbf{Neurocomputing}, vol. 323, pp. 37-51, 2019.}
%
%\item {Zhifei Sun, \textbf{Tinghuan Chen}, You Tong and Meng Zhang. ``Blind Equalization of Constant Modulus Signals Based on Gaussian Process for Classification". \textbf{Wireless Personal Communications}. vol. 97, no. 4, pp. 6005-6018, 2017.}
%
%\item {Chen Zhu, Huatao Zhao, \textbf{Tinghuan Chen} and Tianbo Zhu. ``A low latency and high efficient three-dimension Network-on-Chip based on hierarchical structure". \textbf{Modern Physics Letters B}. vol. 31, no. 19-21, 1740061, 2017.}
%
%\item {\textbf{Tinghuan Chen}, Meng Zhang, Jianhui Wu, Chau Yuen and You Tong. ``Image Encryption and Compression based on Kronecker Compressed Sensing and Elementary Automata Scrambling". \textbf{Optics \& Laser Technology}, vol. 84, pp. 118-133, 2016.}
%
%\item {Meng Zhang, \textbf{Tinghuan Chen}, Xuchao Shi and Peng Cao. ``Image Arbitrary Ratio Down- and Up-Sampling Scheme Exploiting DCT Low Frequency Components and Sparsity in High Frequency Components". \textbf{IEICE Transactions on Information and Systems}. vol. E99-D, no. 2, pp. 475-487, 2016.}
%
%\end{cvitems}
%}







\begin{cventries}
%\cventry
%\cventry


\begin{cvitems}

\footnotesize{

\item {\textbf{Tinghuan Chen}, Bingqing Lin, Hao Geng, Shiyan Hu, Bei Yu, ``Leveraging Spatial Correlation for Sensor Drift Calibration in Smart Building'', accepted by \textbf{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD)}.}

\item {\textbf{Tinghuan Chen}, Qi Sun, Canhui Zhan, Changze Liu, Huatao Yu, Bei Yu, ``Analog IC Aging-induced Degradation Estimation via Heterogeneous Graph Convolutional Networks'', \textbf{IEEE/ACM Asian and South Pacific Design Automation Conference (ASPDAC)}, Tokyo, Jan. 18–21, 2021.}

\item  {Qi Sun, \textbf{Tinghuan Chen}, Siting Liu, Jin Miao, Jianli Chen, Hao Yu, Bei Yu, ``Correlated Multi- objective Multi-fidelity Optimization for HLS Directives Design'', \textbf{IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE)}, Grenoble, Feb. 1–5, 2021.}

\item {\textbf{Tinghuan Chen}, Bingqing Lin, Hao Geng, Bei Yu, ``Smart Building Sensor Drift Calibration'', \textbf{Big Data Analytics for Cyber-Physical Systems}, Springer, 2020: 187-202.}


\item {Qi Sun, \textbf{Tinghuan Chen}, Jin Miao, Bei Yu, ``Power-Driven DNN Dataflow Optimization on FPGA". \textbf{IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}, Westminster, CO, Nov. 4–7, 2019. (Invited Paper)}

\item {\textbf{Tinghuan Chen}, Bingqing Lin, Hao Geng and Bei Yu, ``Sensor Drift Calibration via Spatial Correlation Model in Smart Building", \textbf{ACM/IEEE Design Automation Conference (DAC)}, Las Vegas, NV, June 2-6, 2019.}

\item {Qianru Zhang, Meng Zhang, \textbf{Tinghuan Chen}, Zhifei Sun, Yuzhe Ma and Bei Yu, ``Recent advances in convolutional neural network acceleration", \textbf{Neurocomputing}, vol. 323, pp. 37-51, 2019.}

\item {Qianru Zhang, Meng Zhang, \textbf{Tinghuan Chen}, Jinan Fan, Zhou Yang and Guoqing Li, ``Electricity Theft Detection Using Generative Models", \textbf{IEEE International Conference on Tools with Artificial Intelligence (ICTAI)}, Volos, Nov. 5-7, 2018.}

\item {Zhifei Sun, \textbf{Tinghuan Chen}, You Tong and Meng Zhang, ``Blind Equalization of Constant Modulus Signals Based on Gaussian Process for Classification", \textbf{Wireless Personal Communications}, vol. 97, no. 4, pp. 6005-6018, 2017.}

\item {Chen Zhu, Huatao Zhao, \textbf{Tinghuan Chen} and Tianbo Zhu, ``A low latency and high efficient three-dimension Network-on-Chip based on hierarchical structure", \textbf{Modern Physics Letters B}, vol. 31, no. 19-21, 1740061, 2017.}

\item {\textbf{Tinghuan Chen}, Meng Zhang, Jianhui Wu, Chau Yuen and You Tong, ``Image Encryption and Compression based on Kronecker Compressed Sensing and Elementary Automata Scrambling", \textbf{Optics \& Laser Technology}, vol. 84, pp. 118-133, 2016.}

\item {Meng Zhang, \textbf{Tinghuan Chen}, Xuchao Shi and Peng Cao, ``Image Arbitrary Ratio Down- and Up-Sampling Scheme Exploiting DCT Low Frequency Components and Sparsity in High Frequency Components", \textbf{IEICE Transactions on Information and Systems}, vol. E99-D, no. 2, pp. 475-487, 2016.}


\item {\textbf{Tinghuan Chen}, Zhifang Dong. ``A New Method for the 3-D Discrete Hartley Transform", \textbf{IEEE International Conference on Instrumentation \& Measurement, Computer, Communication and Control}, Harbin, Dec. 8-10, 2012.}

}

\end{cvitems}

\end{cventries}
%\end{cvskills}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Selected Patents}

\begin{cventries}
%\cventry
%\cventry


\begin{cvitems}

\footnotesize{

\item{Meng Zhang, Jingchuan Zhong, Hui Guo, \textbf{Tinghuan Chen}, Ziyang Chen, Jun Liu, ``Reconfigurable modulation and demodulation method used in baseband processing'', PCT/CN2016/073139.}

\item{Meng Zhang, \textbf{Tinghuan Chen}, Zhifei Sun, ``Down-sampling method, up-sampling method, and transmission processing method of video frames'', PCT/CN2016/073415.}

}

\end{cvitems}

\end{cventries}